Galois Characterization of Function Fields of \\ Transcendence Degree $1$ over Number Fields

### 2017-02-10 Master Thesis/synopsis.tex
Add explanation for WLOG in 2.4

\begin{proof}
The degree $[K(\mu_\ell, \sqrt{-1}):K]$ is prime to $\ell$, thus we can assume that $\mu_\ell\subset K$ and $K$ is not formally real with a usual norm argument. Now we can replace $\mathbb{Z}/\ell\mathbb{Z}$ by $\mathbb{Z}/\ell\mathbb{Z}(2) = \mu_\ell^{\otimes 2}$. We write $\mathrm{H}^3(L) = \mathrm{H}^3(L, \mathbb{Z}/\ell\mathbb{Z}(2))$.

>>>>

\begin{proof}
Consider the extension $L=K(\mu_{\ell},\sqrt{-1})/K$. We have the restriction and corestriction map:
\[ \operatorname{res}: \mathrm{H}^3(K,\mathbb{Z}/\ell\mathbb{Z}) \to \mathrm{H}^3(L,\mathbb{Z}/\ell\mathbb{Z}) \qquad \operatorname{cor}:\mathrm{H}^3(L,\mathbb{Z}/\ell\mathbb{Z})\to \mathrm{H}^3(K,\mathbb{Z}/\ell\mathbb{Z}) \]
We have $\operatorname{cor}\circ\operatorname{res} = [L:K]$. Since $[L:K]$ is coprime to $\ell$, we see that $\operatorname{res}$ is injective. The same argument can be made for $K_w(\mu_{\ell},\sqrt{-1})/K_w$. Thus we can assume that $K=L$, i.e. $\mu_{\ell}\subset K$ and $K$ is not formally real. Now we can replace $\mathbb{Z}/\ell\mathbb{Z}$ by $\mathbb{Z}/\ell\mathbb{Z}(2) = \mu_\ell^{\otimes 2}$ and let us write $\mathrm{H}^3(L) = \mathrm{H}^3(L, \mathbb{Z}/\ell\mathbb{Z}(2))$.
